% Resume autogenerated using resume-latex.xsl

\documentclass[letterpaper]{resume}
\usepackage{paralist}
\definecolor{ruleendcolor}{rgb}{0.6, 0.6, 0.6}


    
\author{David Zaebst}
\email{zaebst@gmail.com}    
\phone{(740)412-7333}
\webpage{http://zaebst.com}

  

\begin{document}
\maketitle

\section{Education}


\affiliation[M.A. in Physics]
            {The City College of New York}
            {Degree Conferred February 2013}

\begin{compactitem}
\item   Related Coursework: Quantum Mechanics, Electricity and Magnetism, Statistical Mechanics, and Mathematical Methods for Physics
\end{compactitem}

\affiliation[B.S. in Applied Mathematics and B.A. in Physics]
            {Ohio University}
            {Degrees Conferred June 2006}


\section{Skills}

\begin{compactitem}

\item	Object oriented Perl development
\item	Unix and Linux operating systems
\item	Statistical analysis in Matlab and in Python with NumPy, SciPy, and MatPlotLib
\item	Software build, configuration, and deployment 
\item   Familiar with modern security tools such as Backtrack, Immunity Debugger, Metasploit, and nmap 
\item	Working knowledge of C, C++, Ruby, Python, and SQL

\end{compactitem}

\section{Work History}

\affiliation[Completed Master's Degree]
            {The City College of New York}
            {August 2012-January 2012}


\affiliation[Unix/Linux Systems Administrator]
            {Sumitomo Mitsui Banking Corporation}
            {June 2011-August 2012}

\begin{compactitem}

\item  Worked with Red Hat and AIX severs used for transaction processing and fraud detection software.
\item  Troubleshot issues in a complex environment including Centrify authentication, MQ, MQFTE, Maestro, WebSphere, TSM, ETL, Oracle RAC, and vendor applications.
\item  Coordinated with internal database, networking, and security teams, along with external product vendors to install new applications.
\item  Managed creation of new users, groups, and setup ssh key infrastructure.
\item  Maintained and updated the proprietary build system.  Managed promotion of code from development to production using a centralized source control server. 
\item  Developed Perl libraries packaged as CPAN modules and converted widely deployed packages to RPM packages.  Libraries were designed to lookup the user id specific to an application and environment, launch processes as daemons, and manage the filehandles associated with the processes. 
\item  Reduced application start time for the deposit processing server from 27 minutes to 6 minutes by launching processes in parallel.
\item  Automated application verification procedures that were manually run by operations.  The results were automatically sent in an email report to operations and the application specific team.  
\item  Investigated issues with vendor applications written in C, C++, and Java.  Liaised with vendors to resolve issues with products.  
\item  Utilized common diagnostic tools such as truss, strace, trace, gdb, pstree, lsof, wireshark, and netstat.   
\item  Patched applications and setup environments for user acceptance tests.


\end{compactitem}


\affiliation[Senior Systems Analyst]
            {Morgan Stanley}
            {August 2009-February 2011}

\begin{compactitem}

\item	Maintained and supported seven trading applications with Linux backends and Windows frontends.
\item   Took ownership of technical and trading issues.  Prioritized multiple issues, managed expectations, and ensured resolution.
\item   Troubleshot applications in a large networked environment.  Investigated complaints to determine their root cause from database slowness, network latency, and application logic flaws.
\item   Made Perl modules to query NIS information, convert data to excel format, email reports, and refresh process caches.
\item   Released modules in CPAN package format with perldoc and web documentation detailing their usage.    
\item   Subclassed the Perl DBI to update trading application configurations and financial product information stored in Sybase.  
\item   Worked with Sybase stored procedures to generate trader entitlement reports in excel format.  Utilized LDAP to check departments against expected entitlements.
\item	Added application workflows to the in house application setup system.  The system used a web interface and databases to hold the workflows.  Each workflow ran a set of functions to automate the installation and configuration of an application.
\item   Reconciled financial product records by comparing vendor supplied tables to application tables.  The program added default configurations to new products and removed old products prior to daily process caching.
\item	Repaired and developed commission reports in SQL to show trading and commission data.  Setup user groups to recieve reports and scheduled their runtimes with autosys. 
\item   Enhanced server and application monitoring using proprietary publisher-subscriber libraries.
\item   Built a trade re-reporting tool to query published alerts and resubmit a trade report with needed modifications.
\item   Created tools in Ksh, Zsh, Bash and Perl to query multiple trading processes and aggregate order information.  Included functions to cancel specific orders.
\item   Obtained series 3, 7, 55, and 63 licenses.

\end{compactitem}

\affiliation[Full Time Master's Student]
            {The City College of New York}
            {February 2009-June 2009}


\affiliation[Linux Build Engineer]
            {Bear Stearns / J.P. Morgan}
            {October 2007-February 2009}

\begin{compactitem}

\item   Built and deployed bond calculation libraries on multiple architectures in C and C++ on Linux servers.
\item	Converted XS modules that allow interoperability of Perl with C to function on new servers.
\item 	Rewrote C and C++ test code to work with CUnit and CppUnit testing.   
\item	Installed Cruise Control for continuous integration. Generated configuration XML and Apache Ant files to work with proprietary software build system.
\item	Designed internal web pages with CGI, AJAX, JavaScript, CSS, and HTML for Apache servers.  The pages displayed holiday date changes, and provided documentation.  
\item   Updated programs that convert vendor-supplied financial calendars to internal format.  Added a daily check for new FTP feed arrivals which would download and apply the calendar changes. 
\item	Supported source code control for the fixed income department with proprietary code, CMake, GMake, ClearCase, and SVN.
\item   Configured Apache and SVN to serve source controlled files internally. 
\item	Developed tools in object oriented Perl to troubleshoot C++ builds.  

\end{compactitem}

\affiliation[Systems Analyst]
            {Interactive Brokers}
            {February 2007-October 2007}

\begin{compactitem}

\item	Supported mission critical systems that provide real-time trading on world markets.  
\item	Developed scripts in Perl, Python, and Tk to handle common tasks. 
\item   Troubleshot and repaired data processing routines running on a proprietary Perl scheduler.
\item	Automated monitoring processes, CPU, and memory utilization by remotely connecting through sockets.
\item   Documented bugs in production code and researched their logical causes.

\end{compactitem}


\affiliation[Unix Engineer]
            {American Stock Exchange}
            {September 2006-February 2007}

\begin{compactitem}

\item   Worked on OpenVMS, Fedora Core, HP-UX, and Solaris systems to process market data for the American Stock Exchange.

\end{compactitem}

\end{document}
